A Computational Account of Default-Mode Function\\ by Control Theory and Reinforcement Learning

### 2016-09-27 paper/paper.tex
updates in a train

\begin{abstract}
The default mode network (DMN) is the neural representation of the human
baseline mental activity.
%
Many research streams agree on its likely role in evolutionarily adaptive
envisioning of past and hypothetical scenarios to predict the environment.
The DMN would hence be dedicated to continuous autobiographical memory retrieval,
generation of hypothetical outcomes,
and reward contingency evaluation when letting the mind go.
It explains its highest energy consumption in the brain and
its intimate coupling with conscious awareness.
%
This concept paper proposes a process model that describes
\textit{how} the DMN may actually implement continuous
environmental assessment and prediction.
DMN function is recast from the mathematical perspective of control theory and
reinforcement learning.
Neurobiological evidence on the human and animal DMN
is linked to recent progress in autonomous systems research
in the machine-learning domain.
We argue that this engineering account can parsimoneously
explain a variety of existing neuroscientific hypotheses of DMN function.
%
Formal models of the computational processes subserved by the DMN
could offer statistical control of predictive human behavior.

@@

% official NIPS keywords
\textbf{\\keywords}: Systems Biology, mind wandering, cognitive science,
autonomous learning systems
\textbf{\\Get opinion from}: Danielle Bassett, Kai Vogeley, Mohammad Shakir,
Guillaume Dumas, Smallwood

@@

\section{Introduction}
%
When left unperturbed, the human brain is not at rest.
Rather, the brain continues to metabolize large quantities of
oxygen and glucose energy to maintain inter-neuronal information
transfer in the absence of concrete behavioral goal (Bzdok and Eickhoff, 2016a).
This baseline energy demand is subject to surprisingly little modulations
when mentally processing environmental challenges.
What has early been described as the "stream of consciousness"
in psychology (James, 1890), found its neurobiological manifestation 
in the so-called "default mode network" (DMN) was discovered entirely by accident
(Shulman et al., 1997). This regrouping of some of the highest regions in
the human association cortex (Mesulam et al., 1998) consistently
increased in neural activity during
unfocused everyday mind wandering (Raichle et al., 2001). That is, in
the beginning of the 21st century, brain imaging was the first technology
to allow for the discovery of a unique brain network that subserves a
set of baseline mental activity (Bzdok et al., 2012; Bzdok et al., 2015).

The "default-mode network" (DMN) appeared to be exclusive in task-induced
deactivation during various psychological experiments.
This processing of unknown information categories in the DMN has
been argued to mediate an evolutionarily conserved function for the individual.
This is all the more likely because the DMN contains the two
biggest hotspots of energy consumption in the entire central nervous system.
DMN activity also persists to a substantial degree during the early stages of
sleep (Horovitz et al., 2008) and under anesthesia (Greicius et al., 2008).
Today, many authors believe that the DMN implements
probabilistic estimation of past, hypothetical, and future events. This
brain network
might have emerged to continuously predict environmental events using
mental imagery as an evolutionary advantage.
%
However, information processing in the DMN has also repeatedly
been shown to directly impact human behavior. Goal-directed task performance
improved with decreased activity in default-mode areas (Weissman et al., 2006)
and increased DMN activity was linked to more task-independent,
potentially disturbing thoughts (Mason et al., 2007). 
%
The overarching function of the DMN is mystified by
controlling the interplay between perception–action cycles and
maintaining a baseline contemplations
across time, splace, and content domains at the interface of external world
and self (Bzdok et al., 2015).

Consider an organism faced by choosing the next action
and being informed by rich
reenactment of really happened, hypothetically conceived, and
predicted future events to perfect ongoing decision making.
Control theory is a particularly attractive computational framework
to describe, quantify, and predict the autonomously acting systems,
perhaps including the human brain.
It is known that, the more external world is predictable,
the more mental activity becomes detached from the actual sensory environment
and the more stimulus-independent thoughts occur
(Mason et al., 2007)
that may contribute to optimized control of the organism.
A policy matrix captures the possible action than can be performed
on the environment given a current state. A value matrix 
maps maps expected rewards to environmental objects and events.
Switching between states reduces to a sequential processing model.
In a model-free reinforcement learning approach,
we try to understand the environment always better
starting, at birth, with an environment that initially unknown.
Informed by gradient updates,
the adaptive DMN dynamics learned by feed-back loops
that are calibrated by error occurrence.
Reinforcement learning frameworks can naturally embed DMN function
into the tension between exploitative action with immediate reward and
explorative action with longer-term reward schedules.
The diversity of DMN implications in human cognitive processes
can be parsimoneously recast as minimizing prediction error
and maximizing reward outcome at various time scales.
Such a biologically meaningful optimization objective
may be solved by a stochastic approximation
based on a brain implementation of Markov Chain Monte Carlo sampling
(Tenenbaum2011Science). Even (necessarily imperfect) memories
of past experience, random mind-wandering and dreams during sleep
may be purposeful as building blocks to iteratively improve
the predictive DMN machinery to optimize behavior of the organism.

@@

into the mechanistic relevance of each individual network node
by reviewing experimental neuroscience evidence.

@@

human PMC have been repeated related to

@@

the (external) environmental statistics and its (internal) representation

@@

For instance, Bálint's syndrome is a neurological disorder of conscious
awareness that resulting from damage in the bilateral parietal cortex.
Patients are plaigued by an

@@

The human PMC was congruently coupled in two functional connectivity modalities

@@

of the amygdala (Bzdok et al., 2013b),
which is an amygdalar subregion probably devoted to
continuously scanning environmental input

@@

(Adolphs, 2010; Aggleton et al., 1980; Bzdok et al., 2011; Ghods-Sharifi et al., 2009; LeDoux, 2007).

@@

than by its factual value, based on an internal currency of value

@@

that indicated changes in upcoming trials were
distinct from neuronal firing indicating switching between choices.

@@

The retrosplenial portion of the PMC can subserve evaluation of reward
contingencies and action possibilities by integrating these with

@@

proposed to mediates between the organism's egocentric

@@

statistical knowledge of the environment

@@

that modulate strategic behavioral adjustment in volatile environments
to map possiblity spaces.

The dmPFC subserves predominantly ambiguous amodal processes
across time, space, and content domains in
sensory-independent top-down pathways.
This DMN node has been described as a “mental sketchpad” (Goldman-Rakic, 1996),
potentially implicated in de-novo generation and binding
of meaning representations instructed by stored semantics and memories.
%
The dmPFC may thus enable inference, representation, and assessment
of one's own and other individuals' action and thoughts.
Patients with neurological lesions in the prefrontal cortex
are now to adapt to novel situations and stimuli with difficulty
(Stuss, D. T. \& Benson, D. F. The Frontal Lobes, Raven, New York, 1986).
Specifically, neural activity in human dmPFC
reflected expectations about other peoples actions and errors thereof
(Suzuki et al., 2012; van Schie et al., 2004).
dmPFC activity indeed explained the proficiency decline
of inferring other peoples thoughts in the elderly (Moran et al., 2012).
Some dmPFC neurons in macaque monkeys exhibited a preference
for processing others', rather than own, behavior
with fine-grained adjustment of contextual circumstances (Yoshida et al., 2011).
%
Such highly abstract neural computations necessarily rely on the
generation of probabilistic internal information drawing from
episodic memory retrieval, non-mnemonic scene construction processes,
and explicit knowledge of the external world.
%
According to computational neuroimaging experiments,
the dmPFC activity preferentially models stimulus-value associations of
possible actions that are not actually executed,
whereas the vmPFC activity models value in the environment that leads performed actions
{Nicolle, 2012 \#3750}.

The vmPFC subserves less ambiguous subjective-value-related evaluative processes
reward-informed and risk estimation of self-relevant environmental stimuli.
This DMN node is more closely associated with
orchestrating adapted behavior by bottom-up-driven
processing of “what matters now”.
Quantative lesion findings across  344 human individuals confirmed
a gross impairment in value-based decision making
(Glaescher et al., 2016).
The vmPFC is preferentially connected with limbic and reward-related areas.
The vmPFC has been observed to have monosynap- tical connections with the ventral striatum (VS, which anatom- ically includes the NAc) in axonal tracing studies in monkeys (Haber et al., 1995; Ferry et al., 2000).
The NAc is thought to be linked to reward mechanisms that may not only modulate motivated behavior towards basic survival needs, but also
subserve model-free reinforcement learning in humans more broadly
(O'Doherty 2015).
This is consistent with diffusion MRI (dMRI) tractography in humans and monkeys (Croxson et al., 2005) that quantified the VS to be substantially more likely connected to the vmPFC than dmPFC in both species.
Two functional connectivity modalities in humans strongly connected
the vmPFC with the nucleus accumbens (NAc), hippocampus (HC),
posterior cingulate cortex (PCC), and retrosplenial cortex (RSC).
%
The vmPFC is often proposed to be involved in (external) emotional
reactions and own (visceral) arousal.
Real or imaginged bodily states could be mapped in the vmPFC
as a bioregulatory disposition governing cognition
and decision making (Damasio, 1996; Nauta, 1971)
In studies of decision making and neuroeconomics, ventromedial prefrontal cortex (vmPFC) con- sistently reflects an individual’s subjective valuation (Behrens et al., 2008; Boorman et al., 2009; Knutson et al., 2005; Plass- mann et al., 2007)
This may be why performance within and across participants
was related to state encoding in OFC.
Such a “cognitive map” of action space was argued to encode
the current task state even when states are unobservable from sensory input,
which was shown to be critical for behavior.
The GMV of the vmPFC and VS correlated with indices of social reward attitudes and value-guided behavior (Lebreton et al., 2009).
Additionally,
independent whole-brain analyses from structural
neuroimaging studies related the gray-matter volume (GMV) of the vmPFC
(more consistently than any other
brain region) to indices of
social competence and social network complexity,
among the most complicated decision that humans and monkeys take
(Lebreton et al., 2009; Powell et al., 2010; Lewis et al., 2011; Sallet et al., 2011).
%

The HC is well known to be involved in memory and
spatial navigation in animals and humans
(von Bechterew, 1900; Scoville and Milner, 1957; O’Keefe and Dostrovsky, 1971; Maguire et al., 2000).
Its highly recursive anatomical architecture
may be specifically designed to allowing reconstruction
whole episode of experience from memory fragments.
%
While the HC in the medial temporal lobe system
is traditionally believed to allow remembering the past,
there is now increasing evidence for a role
in constructing mental models in general (Schachter/Buckner).
Indeed,
hippocampal damage [21,38–40] is
not only associated with an impairment in reexperiencing the past (i.e., amnesia),
but also thinking about one’s own future and
imagining new fictitious experiences more broadly (Hassabis/PNAS).
Mental scenes created by hippocampus-lesioned patients exposed a lack of
spatial integrity, richness in detail, and overall coherence.
%
Single-cell recordings in the animal hippocampus revealed
some constantly active neuronal ensembles whose firing coincided with
distinct locations in space while the animal navigated through its surroundings.
London taxi drivers, individuals with high performance in spatial navigation,
were shown to exhibit increased grey matter volume in the
posterior hippocampus (Maguire et al. 2006b).
But encoding and generative reconstruction in the hippocampus extends
beyond mere spatial knowledge of the environment.
Based on large-scale recordings of hippocampal neuronal populations,
complex spiking patterns can be followed across extended periods including
their modification of input-free self-generated patterns
after environmental events (buszaki2004 theta oscillations).
Specific spiking sequences, that were elicited in experimental task conditions,
have been shown to be reenacted spontaneously during sleep.
Moreover, spike sequences measured in hippocampal place cells of rats
featured reoccurred directly after experimental trials
as well as directly before upcoming experimental trials (Diba + Buzsaki 2007).
Such hippocampal ensemble burts during rest and sleep
have been proposed to be critical in communicating local information
to the neocortex for long-term storage, which includes the DMN.
These mechanisms of the hippocampus probably make important contributions to the
recollection of autobiographical memory episodes and other
reexperienced or newly generated mental scenarios (Hassabias2007).
%
The HC thus orchestrates elements of experienced environmental aspects for
consolidations based on reenactment and for integration into 
rich mental scene construction. In this view, the HC my even influence
ongoing perception in the current environment (Maguire 2016).
-> self-play in deepmind Go
-> Kai had an interesting idea: the deja-vu effect could be when you already accidentally perturbed past such that it really occures in reality later

Finally,
the right and left TPJ are known to have hemispheric differences
according to their cytoarchitectonic borders and gyrification pattern
(Caspers et al., 2008; Caspers et al., 2006).
Neuroscientific investigations on hemispheric functional specialization
have converged to the right versus left cerebral hemisphere as dominant for
attention versus language functions (Broca 1865, Wernicke 1874, Lichtheim 1885;
Gazzaniga, Bogen et al. 1965, Sperry 1982, Stephan, Marshall et al. 2003).
%
The aRTPJ is a key node network is central for
action initiation during externally structured tasks and
sensorimotor control by integrating supramodal stimulus-guided attention
(Corbetta et al., 2002).
Involvement of this DMN node was repeatedly reported in
visuo-proprioceptive conflict (Balslev et al., 2005) and
multi-modal detection of sensory changes across
visual, auditory, or tactile stimulation in a multi-modal fMRI study
(Downar et al., 2000).
In humans, direct electrical stimulation of the
RTPJ during neurosurgery was associated with altered perception
and stimulus awareness (Blanke et al., 2002).
%
Importantly, the RTPJ has been shown to be intimately related to
supramodal prediction error signaling.
Neural activity in the RTPJ has been argued to be responsible 
for stimulus-driven attentional reallocation to 
salient and surprising sources of information
as a ‘‘circuit breaker’’ that recalibrates control and maintenance systems
(Bzdok et al., 2013; Corbetta et al., 2008).
Indeed, patients with right TPJ damage have particular difficulties
with multistep actions (Hartmann et al. 2005).
In the face of large discrepancies between actual and previously predicted
environmental events the RTPJ acts a potential switch between
externally-oriented mind sets focussed on the
sensory world and internally-oriented mind sets focussed
on self-relevant mind-wandering of possible mental scenarios.
Transient RTPJ in humans for instance disrupted the
impact of predicted intentions of other individuals (Young et al. 2010b),
a capacity believed to be subserved by the DMN.
The RTPJ might hence be an important player that shifts away
from the default active ‘‘internally directed’’ processes
to deal instead with immediate environmental objects and contexts.
-> (slow) endogeneous changes in state transitions by the policy and value matrices
For example, the alarm at the museum is not part of the task set of listening to the guide’s discussion of Hieronymous Bosch, but it is clearly a behaviourally relevant stimulus. <=> MCMC in HC / PCC

>>>>

\begin{abstract}
The default mode network (DMN) is the neural representation of the human
baseline mental activity.
%
Many research streams agree on its likely role in evolutionarily adaptive
envisioning of past and hypothetical scenarios to predict the environment.
The DMN would hence be dedicated to continuous autobiographical memory retrieval,
generation of hypothetical outcomes,
and reward contingency evaluation when letting the mind go.
It explains its highest energy consumption in the brain and
its intimate coupling with conscious awareness.
%
This concept paper proposes a process model that describes
\textit{how} the DMN may actually implement continuous
environmental assessment and prediction.
DMN function is recast in mathematical terms
from the perspective of control theory and
reinforcement learning.
Neurobiological evidence on the human and animal DMN
is linked to recent progress in autonomous systems research
in the machine-learning domain.
We argue that this engineering approach to DMN function can parsimoneously
explain a variety of existing neuroscientific hypotheses.
%
Formal models of the computational processes subserved in the DMN
could offer statistical control of predictive human behavior.

@@

% official NIPS keywords
\textbf{\\keywords}: Systems Biology, mind wandering, cognitive science,
autonomous learning systems
\textbf{\\Get opinion from}: Danielle Bassett, Kai Vogeley, Mohammad Shakir,
Guillaume Dumas, Smallwood, Tenenbaum

@@

\section{Introduction}
%
When left unperturbed, the human brain is not at rest.
Rather, the brain continues to metabolize large quantities of
oxygen and glucose energy to maintain inter-neuronal information
transfer in the absence of a focused behavioral goal (Raichle 2001;
Shulman, 1999).
This baseline energy demand is subject to surprisingly little modulations
when mentally processing environmental challenges
(Bzdok and Eickhoff, 2016a).
What has early been described as the "stream of consciousness"
in psychology (James, 1890), found its neurobiological manifestation 
in the so-called "default mode network" (DMN)
(Shulman et al., 1997). This networked collection of some of the highest regions in
the human association cortex (Mesulam et al., 1998) consistently
increased in neural activity during
unfocused everyday mind wandering (Raichle et al., 2001). That is, in
the beginning of the 21st century, brain imaging was the first technology
to allow for the discovery of a unique brain network that subserves
baseline mental activity (Bzdok et al., 2012; Bzdok et al., 2015).

The DMN appeared to be exclusive in task-induced
deactivation during various psychological experiments.
This processing of unknown information categories in the DMN has
been argued to mediate an evolutionarily conserved function for the individual.
This is all the more likely because the DMN contains the two
biggest hotspots of energy consumption in the entire central nervous system.
DMN activity also persists to a substantial degree during
sleep (Horovitz et al., 2008) and under anesthesia (Greicius et al., 2008).
Today, many authors believe that the DMN implements
probabilistic estimation of past, hypothetical, and future events. This
brain network
might have emerged to continuously predict environmental events using
mental imagery as an evolutionary advantage.
%
However, information processing in the DMN has also repeatedly
been shown to directly impact human behavior. Goal-directed task performance
improved with decreased activity in default-mode areas (Weissman et al., 2006)
and increased DMN activity was linked to more task-independent,
yet sometimes useful thoughts (Mason et al., 2007; Seli et al., 2016). 
%
Understanding of the overarching DMN function is complicated by
simultaneously controlling perception–action cycles and
maintaining baseline contemplations
across time, splace, and content domains
interfacing the external world and the self.

Consider an agent faced by choosing the next action
and being guided by rich
reenactment of really happened, hypothetically conceived, and
predicted future events to perfect ongoing behavioral performance.
A particularly attractive computational framework
to describe, quantify, and predict autonomously acting systems like the brain
can be the combination of control theory and reinforcement learning.
It is known that, the more the external world is predictable,
the more mental activity becomes detached from the actual sensory environment
and the more stimulus-independent thoughts occur
(Mason et al., 2007).
These "offline" processes may however contribute to optimized control of the organism.
We formalize
a policy matrix to capture the space of possible actions that can be performed
on the environment given the current state. A value matrix 
maps maps expected rewards to environmental objects and events.
Switching between states reduces to a sequential processing model.
In a model-based reinforcement learning approach,
we try to understand the environment always better
starting, at birth, with an environment that is completely unknown.
Informed by outcomes of performed action,
the DMN dynamics are constantly adapted in feed-back loops
that are calibrated by error occurrence.
A DMN framework incorporating reinforcement learning
can naturally embed human behavior
into the tension between exploitative action with immediate gains and
explorative action with longer-term reward schedules.
The implication of the DMN in a diversity of human cognitive processes
can be parsimoneously recast as minimizing prediction error
based on pervasive probabilistic simulations,
thus maximizing reward outcome at various time scales.
Such a purposeful optimization objective
may be solved by a stochastic approximation
based on a brain implementation of Markov Chain Monte Carlo sampling
(Tenenbaum2011Science). Even (necessarily imperfect) memories
of past experience, random mind-wandering and dreams during sleep
may provide meanginful building blocks to iteratively improve
the predictive DMN machinery to optimize the behavior of the organism.

@@

by the mechanistic relevance of each individual network node
based on published evidence from neuroscience experiments.

@@

human PMC have been repeatedly related to

@@

the environmental statistics and its internal representation

@@

For instance, B\'alint's syndrome is a neurological disorder of conscious
awareness that results from damage in the bilateral parietal cortex.
Patients are plagued by an

@@

Congruently,
the human PMC was coupled in across two functional connectivity modalities

@@

of the amygdala (Bzdok et al., 2013b).
This amygdalar subregion has been proposed to
continuously scan environmental input

@@

(Adolphs, 2010; Aggleton et al., 1980; Bzdok et al., 2011;
Ghods-Sharifi et al., 2009; LeDoux, 2007).

@@

than by its factual value, based on an internal currency of value.

@@

indicated changing choices in upcoming trials and their neural patterns were
distinct from spike firings that indicated choosing either option.

@@

The retrosplenial portion of the PMC can subserve action possibilities
and evaluation of reward contingencies by integrating these with

@@

proposed to mediate between the organism's egocentric

@@

statistical assessment of the environment

@@

that modulate strategic behavioral adjustment in volatile environments.

The dmPFC subserves predominantly ambiguous amodal processes
across time, space, and content domains in
sensory-independent top-down pathways.
This DMN node has been described as a “mental sketchpad” (Goldman-Rakic, 1996),
potentially implicated in de-novo generation and binding
of meaning representations instructed by stored semantics and memories.
%
The dmPFC may thus enable inference, representation, and assessment
of one's own and other individuals' action and thoughts.
Patients with neurological lesions in the prefrontal cortex
are known to adapt to novel situations and stimuli with difficulty
(Stuss, D. T. \& Benson, D. F. The Frontal Lobes, Raven, New York, 1986).
Specifically, neural activity in human dmPFC
reflected expectations about other peoples actions and errors thereof
(Suzuki et al., 2012; van Schie et al., 2004).
dmPFC activity indeed explained the proficiency decline
of inferring other peoples thoughts in the elderly (Moran et al., 2012).
Some dmPFC neurons in macaque monkeys exhibited a preference
for processing others', rather than own, behavior
with fine-grained adjustment of contextual circumstances (Yoshida et al., 2011).
%
Such highly abstract neural computations necessarily rely on the
generation of probabilistic internal information drawing from
episodic memory retrieval, generative construction processes,
and explicit knowledge of the external world.
%
According to computational neuroimaging experiments,
the dmPFC activity preferentially models stimulus-value associations of
possible actions that are not actually executed,
whereas the vmPFC activity models value in the environment that leads performed actions
{Nicolle, 2012 \#3750}.

The vmPFC subserves less ambiguous subjective-value-related evaluative processes
reward-informed and risk estimation of self-relevant environmental stimuli.
This DMN node is more closely associated with
orchestrating adapted behavior by bottom-up-driven
processing of “what matters now”.
Quantative lesion findings across 344 human individuals confirmed
a gross impairment in value-based decision making
(Glaescher et al., 2016).
The vmPFC is preferentially connected with limbic and reward-related areas.
The vmPFC has been observed to have monosynaptical connections
with the nucleus accumbens
in axonal tracing studies in monkeys (Haber et al., 1995; Ferry et al., 2000).
The NAc is thought to be linked to reward mechanisms that not
only modulate motivated behavior towards basic survival needs but also
subserve reinforcement learning in humans more broadly
(O'Doherty 2015).
This is consistent with diffusion MRI (dMRI) tractography in humans and monkeys
(Croxson et al., 2005) that
quantified this brain regions to
be substantially more likely connected to the vmPFC than dmPFC in both species.
Two functional connectivity modalities in humans strongly connected
the vmPFC with the nucleus accumbens, hippocampus (HC),
and posteriomedial cortex.
%
The vmPFC is often proposed to be involved in (external) emotional
reactions and own (visceral) arousal.
Real or imaginged bodily states could be mapped in the vmPFC
as a bioregulatory disposition governing cognition
and decision making (Damasio, 1996; Nauta, 1971)
In neuroeconomic studies of human decision making,
the vmPFC consistently reflects an individual’s subjective
valuation (Behrens et al., 2008; Boorman et al., 2009; Knutson et al., 2005; Plassmann et al., 2007)
This may be why performance within and across participants
was related to state encoding in OFC.
Such a “cognitive map” of action space was argued to encode
the current task state even when states are unobservable from sensory input,
which was shown to be critical for behavior.
The GMV of the vmPFC and nucleus accumbens
correlated with indices of social reward attitudes and
value-guided behavior (Lebreton et al., 2009).
Additionally,
independent whole-brain analyses from structural
neuroimaging studies related the gray-matter volume GMV of the vmPFC,
more consistently than any other
brain region, to indices of
social competence and social network complexity,
among the most complicated decision that humans and monkeys take
(Lebreton et al., 2009; Powell et al., 2010; Lewis et al., 2011; Sallet et al., 2011).
%

The HC is well known to be involved in memory and
spatial navigation in animals and humans
(von Bechterew, 1900; Scoville and Milner, 1957; O’Keefe and Dostrovsky, 1971; Maguire et al., 2000).
Its highly recursive anatomical architecture
may be specifically designed to allow reconstructing
entire episodes of experience from memory fragments.
%
While the HC in the medial temporal lobe system
is traditionally believed to allow remembering the past,
there is now increasing evidence for a role
in constructing mental models in general (Schachter/Buckner;
Maguire 2016).
Indeed,
hippocampal damage is
not only associated with an impairment in reexperiencing the past (i.e., amnesia),
but also thinking about one’s own future and
imagining new fictitious experiences more broadly (Hassabis/PNAS).
Mental scenes created by hippocampus-lesioned patients exposed a lack of
spatial integrity, richness in detail, and overall coherence.
%
Single-cell recordings in the animal hippocampus revealed
some constantly active neuronal ensembles whose firing coincided with
distinct locations in space while the animal navigated through its surroundings.
London taxi drivers, individuals with high performance in spatial navigation,
were shown to exhibit increased grey matter volume in the
posterior hippocampus (Maguire et al. 2006b).
But encoding and generative reconstruction in the hippocampus extends
beyond mere spatial knowledge of the environment.
Based on large-scale recordings of hippocampal neuronal populations,
complex spiking patterns can be followed across extended periods including
their modification of input-free self-generated patterns
after environmental events (buszaki2004 theta oscillations).
Specific spiking sequences, that were elicited in experimental task conditions,
have been shown to be reenacted spontaneously during sleep.
Moreover, spike sequences measured in hippocampal place cells of rats
featured reoccurrence directly after experimental trials
as well as directly before upcoming experimental trials (Diba + Buzsaki 2007).
Such hippocampal ensemble burts during rest and sleep
have been proposed to be critical in communicating local information
to the neocortex for long-term storage, potentially also in the DMN.
These mechanisms of the hippocampus probably make important contributions to the
recollection of autobiographical memory episodes and other
reexperienced or newly generated mental scenarios (Hassabias2007).
%
The HC thus orchestrates elements of experienced environmental aspects for
consolidations based on reenactment and for integration into 
rich mental scene construction. In this view, the HC my even influence
ongoing perception in the current environment (Maguire 2016).
-> self-play in deepmind Go
-> Kai had an interesting idea: the deja-vu effect could be when you already accidentally perturbed past such that it really occures in reality later

Finally,
the right and left TPJ are known to have hemispheric differences
according to their cytoarchitectonic borders and gyrification pattern
(Caspers et al., 2008; Caspers et al., 2006).
Neuroscientific investigations on hemispheric functional specialization
have converged to the right versus left cerebral hemisphere as dominant for
attention versus language functions (Broca 1865, Wernicke 1874, Lichtheim 1885;
Gazzaniga, Bogen et al. 1965, Sperry 1982, Stephan, Marshall et al. 2003).
%
The aRTPJ is a key node network is central for
action initiation during externally structured tasks and
sensorimotor control by integrating supramodal stimulus-guided attention
(Corbetta et al., 2002).
Involvement of this DMN node was repeatedly reported in
visuo-proprioceptive conflict (Balslev et al., 2005) and
multi-modal detection of sensory changes across
visual, auditory, or tactile stimulation in a multi-modal fMRI study
(Downar et al., 2000).
In humans, direct electrical stimulation of the
RTPJ during neurosurgery was associated with altered perception
and stimulus awareness (Blanke et al., 2002).
%
Importantly, the RTPJ has been shown to be intimately related to
supramodal prediction and error signaling.
Neural activity in the RTPJ has been argued to be responsible 
for stimulus-driven attentional reallocation to 
salient and surprising sources of information
as a ‘‘circuit breaker’’ that recalibrates control and maintenance systems
(Bzdok et al., 2013; Corbetta et al., 2008).
Indeed, patients with right TPJ damage have particular difficulties
with multistep actions (Hartmann et al. 2005).
In the face of large discrepancies between actual and previously predicted
environmental events the RTPJ acts a potential switch between
externally-oriented mind sets focussed on the
sensory world and internally-oriented mind sets focussed
on self-relevant mind-wandering of possible mental scenarios.
Transient RTPJ in humans for instance disrupted the
impact of predicted intentions of other individuals (Young et al. 2010b),
a capacity believed to be subserved by the DMN.
The RTPJ might hence be an important player that shifts away
from the default active ‘‘internally directed’’ processes
to deal instead with immediate environmental objects and contexts.
-> (slow) endogeneous changes in state transitions by the policy and value matrices
For example, the alarm at the museum is not part of the task set of listening to the guide’s discussion of Hieronymous Bosch, but it is clearly a behaviourally relevant stimulus. <=> MCMC in HC / PCC
